A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
remove paragraph from evaluation

We evaluate with DT sessions taking $b_0$ admitting between 20 and 200
abstract states with non-zero probability. We run 50 simulations in
each configuration, and have a timeout on each simulation of 30
minutes (1800 seconds)\footnote{All experiments were conducted on a
  2.3GHz AMD Opteron using one CPU core.}. The continual planning
times are reported in Figure~\ref{fig:results-time}, and the quality
data in Figure~\ref{fig:results-quality}.
%%
For Items~$a$-$e$ the goal is to find objects and report their
position to a user. In some cases there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment. Item~$f$ reports for tasks requiring indirect sensing,
where the robot must relocate to a room with a particular category
(e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
so is omitted from that reporting.  Because reward is only allocated
once, on the achievement of the goal,  we find it
intuitive to report average plan costs and the success rates in
problems that admit a solution (i.e., positive reward scaled by a
constant factor).

@@

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{pomdp-quality}\hfill
  \includegraphics{pomdp-solvable-quality}\hfill
  \includegraphics{dora2-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora56-quality}\hfill
  % \vspace{2mm}
  % \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs.}
  \label{fig:results-quality}
\end{figure}

>>>>

We evaluate with DT sessions taking $b_0$ admitting between 20 and 200
abstract states with non-zero probability. We run 50 simulations in
each configuration, and have a timeout on each simulation of 30
minutes (1800 seconds)\footnote{All experiments were conducted on a
 2.66GHz Intel Xeon X5355 CPU using one CPU core.}. The continual planning
times are reported in Figure~\ref{fig:results-time}, and the quality
data in Figure~\ref{fig:results-quality}.
%%
For Items~$a$-$e$ the goal is to find objects and report their
position to a user. In some cases there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment. 
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.

Because reward is only allocated
once, on the achievement of the goal,  we find it
intuitive to report average plan costs and the success rates in
problems that admit a solution (i.e., positive reward scaled by a
constant factor).

@@

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{pomdp-quality}\hfill
  % \includegraphics{pomdp-solvable-quality}\hfill
  \includegraphics{dora2-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora56-quality}\hfill
  % \vspace{2mm}
  % \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs.}
  \label{fig:results-quality}
\end{figure}
